### 2017-01-16 MSSM/MSSM.tex
Adding a few more figs to MSSM chapter

In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on 12.9 fb$^{-1}$ collected
at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the two modes (see THEORY) and decay into $\Pgt\Pgt$. The gluon fusion
production mode will also be referred to as gg$\phi$, and the b-associated production
mode will be referred to as bb$\phi$. In 
addition to the upper limits on cross--section times branching ratio of these two processes, 
the results are interpreted in MSSM benchmark scenarios and 2D likelihood
scans of the two production modes are performed. A very similar analysis
was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
As it is so similar to the analysis performed on the 2016 dataset it
will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

\begin{equation}\label{eqn:wjets_ss_norm}
\begin{split}
N_{\text{data}}^{SS, \text{high } m_{\text{T}}} - N_{\text{other}}^{SS,
\text{high } m_{\text{T}}} & =
N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} + N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
N_{\text{data}}^{OS, \text{high } m_{\text{T}}} - N_{\text{other}}^{OS,
\text{high } m_{\text{T}}} & = N_{\text{QCD}}^{OS, \text{high } m_{\text{T}}} +
N_{W}^{OS, \text{high } m_{\text{T}}} \\
& = R_{\text{QCD}}^{OS/SS}\cdot N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} +
R_{W}^{OS/SS} \cdot N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
\Rightarrow N_{W}^{SS, \text{high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{OS,
\text{high } m_{\text{T}}}  - N_{\text{other}}^{OS, \text{high } m_{\text{T}}}  -
R_{\text{QCD}}^{OS/SS}\cdot(N_{\text{data}}^{SS, \text{high } m_{\text{T}}}  -
N_{\text{other}}^{SS, \text{high } m_{\text{T}}} )}{R_{W}^{OS/SS} -
R_{\text{QCD}}^{OS/SS}} ,
\end{split}
\end{equation}

where $R_{W}^{OS/SS}$ is the ratio between opposite-sign and same-sign \Wjets events
and $R_{QCD}^{OS/SS}$ the ratio between opposite-sign and same-sign QCD events. Using 
equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
opposite-sign, high \mT~region is given by $R_{W}^{OS/SS}\cdot N_{W}^{SS,\text{high} m_{T}}$. 
This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:

\begin{equation}\label{eqn:wjets_os_norm}
N_{W}^{OS,\text{low} m_{T}} = \frac{N_{W,MC}^{OS,\text{low} m_{T}}}{N_{W,MC}^{OS,\text{high} m_{T}}}\cdot R_{W}^{OS/SS} \cdot N_W^{SS,\text{high }m_{T}},
\end{equation}

@@

The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{W}^{OS/SS}$ is 
taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
is close to 1.

The method described so far works well in the no b-tag categories, but in the b-tag category
the \ttbar background dominates. For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements still stand. Events with at least one 
jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in the 1-jet selection, multiplied by an extrapolation factor 
$\frac{N_{W,MC}^{OS,\text{low } m_{T},\text{b-tag category}}}{N_{W,MC}^{OS,\text{low }m_{\text{T}},\text{1-jet selection}}}$ ADD FIGURES

\subsubsection{QCD OS/SS ratio}
\label{sec:mssm_bkgs_etmt_qcdosss}
The ratio of opposite--sign to same--sign QCD events, $R_{QCD}^{OS/SS}$ is measured
in two anti-isolated sidebands by performing a fit to the distribution of the
visible mass of the di-tau pair in 
opposite-sign events. The QCD template, which is taken from same--sign events 
assuming $R_{QCD}^{OS/SS} = 1$ is treated as the signal, and a binned maximum
likelihood fit to the QCD signal strength is performed while allowing the other
backgrounds to float within reasonable normalisation uncertainties. The
resulting best fit value of the signal strengh parameter is taken as $R_{QCD}^{OS/SS}$.
Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\mu}<0.25$ and $0.1<I_{\text{rel}}^{e}<0.2$)
and one further away ($0.25<I_{\text{rel}}^{\mu}<0.5$ and $0.2<I_{\text{rel}}^{e}<0.5$). The results of the fits,
performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_far}
for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
$R_{QCD}^{OS/SS}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
an overall uncertainty of 12\% in the \etau channel and 4\% in the \mutau channel.
When performing the same fits in the no b-tag and b-tag categories to determine differences between
this pre-categorisation opposite--sign to same--sign ratio, and the ratio as measured in categories it is found that 
the fit is not stable in the b-tag category due to the number of events in this region being too small.
The uncertainty on the ratio is increased for the b-tag category to cover the differences.
The uncertainties are already large enough to cover differences between the pre-categorisation $R_{QCD}^{OS/SS}$ and the
fits as performed in the no b-tag category. So $R_{QCD}^{OS/SS}$ in the \mutau channel is taken to be
1.18 in both the b-tag and the no b-tag category, with a 60\% uncertainty in the b-tag category and a 4\% uncertainty in the no b-tag category.
In the \etau channel $R_{QCD}^{OS/SS}$ is taken to be 1.02 with a 60\% uncertainty in the b-tag category and a 12\% uncertainty
in the no b-tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.180$\pm$0.044.}
\label{fig:mssm_qcdossss_mtnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.184$\pm$0.035.}
\label{fig:mssm_qcdossss_mtfar}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.015$\pm$0.059.}
\label{fig:mssm_qcdossss_etnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.127$\pm$0.045.}
\label{fig:mssm_qcdossss_etfar}
\end{figure}

\subsubsection{QCD normalisation}
\label{sec:mssm_bkgs_etmt_qcdnorm}
The QCD normalisation is estimated by inverting the opposite-sign requirement
of the di-tau pair in the signal region. The yield is taken from the same--sign
region with otherwise identical cuts to the opposite--sign region. The contributions
from other backgrounds in this region are subtracted to give an estimate of the number
of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
expected in this region is given by
\begin{equation}\label{eqn:wjets_qcdsub}
N_{W,SS SR} = \frac{N_{MC,SS SR}}{N_{MC,SS high mT}}N_{W,SS high mT}
\end{equation}

@@

\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
\label{sec:mssm_bkgs_qcd_tt}
In the \tautau channel the QCD background is by far the 
dominant background. The normalisation and shape 
of this background are estimated from a sideband with loosened 
isolation requirements with respect to the signal region. 
In the no b-tag category the sideband used is determined
by having the tau with highest \pT~ pass the tight working
point of the tau ID discriminator, as in the nominal selection.
The other hadronic tau in the pair does not pass the tight working point,
but does pass the medium working point. This sideband is 
chosen as it is as close to the signal region as possible, and 
this should minimise biases in the shape of the total transverse mass
distribution. Other backgrounds
in this sideband are subtracted from the observation to give
the QCD estimate. Differences in normalisation due to
the use of a loosened sideband are corrected for by loose-to-tight isolation
scale factor. This correction factor is measured as
\begin{equation}\label{eqn:tautau_qcd}
R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{obs}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{obs}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
\end{equation}

So this takes the ratio between the observed data with other
backgrounds subtracted in the region equivalent to the signal region, but with the
charge requirement of the pair inverted, and the region equivalent to the sideband
with loosened isolation but with the charge requirement on the pair inverted.

An analogous method is used for this estimate in the 
b-tag category, however, the sideband as used for the 
no b-tag category does not contain enough events to 
provide a background estimate. Therefore a sideband where
the highest \pT~tau passes the tight working point of the
tau ID discriminator, and the other tau passes the loose working
point of the discriminator, but not the tight working point, is used.
This sideband is slightly further away from the signal region than the
'tight--medium' sideband INSERT FIGURE. The bias from using this looser
sideband has been assessed and has a less than 1$\sigma$ effect.
FIXME THIS ISN'T VERY USEFUL INFO!

@@

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}. As the 
shape of the total transverse mass distribution depends on the energy of the $\Pgt_{h}$
it is applied as a shape uncertainty. It is applied to the signal samples and to
backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
hadronic taus.
\subsubsection*{Electron energy scale}
The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This affects
the shape of the total transverse mass distribution, and this uncertainty is applied to the
signals and to the \Ztautau background.
\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
is applied to account for the extrapolation from the tau ID efficiency
measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s. This
uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels
\subsubsection*{Top quark \pT~ reweighting}
To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape
uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
of the correction, ie the difference between applying the correction twice and not applying the correction at all.
\subsubsection*{Drell-Yan shape reweighting}
An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
On the \Wjets background in the \etau and \mutau channels a shape 
uncertainty of $\frac{-20\% \times p_{\text{T}}}{\text{GeV}}$ is 
applied. This uncertainty is derived from variations in the data/MC ratio
for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~ in 
\Wjets events \cite{CMS-PAS-HIG-16-037}.

>>>>

In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset corresponding to
an integrated luminosity of 12.9 fb$^{-1}$ collected
at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the two modes (see THEORY) and decay into $\Pgt\Pgt$. The gluon fusion
production mode will also be referred to as gg$\phi$, and the b-associated production
mode will be referred to as bb$\phi$. In 
addition to the upper limits on cross--section times branching ratio of these two processes, 
the results are interpreted in MSSM benchmark scenarios and 2D likelihood
scans of the two production modes are performed. A very similar analysis
was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
As it is so similar to the analysis performed on the 2016 dataset it
will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

\begin{equation}\label{eqn:wjets_ss_norm}
\begin{split}
N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
 high } m_{\text{T}}} & =
N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} + N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
 high } m_{\text{T}}} & = N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
N_{\text{W}}^{\text{OS, high } m_{\text{T}}} \\
& = R_{\text{QCD}}^{\text{OS/SS}}\cdot N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} +
R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{\text{OS,
 high } m_{\text{T}}}  - N_{\text{other}}^{\text{OS, high } m_{\text{T}}}  -
R_{\text{QCD}}^{\text{OS/SS}}\cdot(N_{\text{data}}^{\text{SS, high } m_{\text{T}}}  -
N_{\text{other}}^{\text{SS, high } m_{\text{T}}} )}{R_{\text{W}}^{\text{OS/SS}} -
R_{\text{QCD}}^{\text{OS/SS}}} ,
\end{split}
\end{equation}

where $R_{\text{W}}^{\text{OS/SS}}$ is the ratio between opposite-sign and same-sign \Wjets events
and $R_{\text{QCD}}^{\text{OS/SS}}$ the ratio between opposite-sign and same-sign QCD events. Using 
equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS,high} m_{T}}$. 
This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:

\begin{equation}\label{eqn:wjets_os_norm}
N_{\text{W}}^{\text{OS, low} m_{T}} = \frac{N_{\text{W,MC}}^{\text{OS, low} m_{T}}}{N_{\text{W,MC}}^{\text{OS, high} m_{T}}}\cdot R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high }m_{T}},
\end{equation}

@@

The use of the method presented relies on knowledge of $R_{\text{W}}^{\text{OS/SS}}$,
$R_{\text{QCD}}^{\text{OS/SS}}$, and on these two ratios not being too similar to each other. 
The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti--isolated
control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
is close to 1.

The method described so far works well in the no b-tag categories, but in the b-tag category
the \ttbar background dominates. For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements still stand. Events with at least one 
jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in the 1-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$

\subsubsection{QCD OS/SS ratio}
\label{sec:mssm_bkgs_etmt_qcdosss}
The ratio of opposite--sign to same--sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$ is measured
in two anti-isolated sidebands by performing a fit to the distribution of the
visible mass of the di-tau pair in 
opposite-sign events. The QCD template, which is taken from same--sign events 
assuming $R_{\text{QCD}}^{\text{OS/SS}} = 1$ is treated as the signal, and a binned maximum
likelihood fit to the QCD signal strength is performed while allowing the other
backgrounds to float within reasonable normalisation uncertainties. The
resulting best fit value of the signal strengh parameter is taken as $R_{\text{QCD}}^{\text{OS/SS}}$.
Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\mu}<0.25$ and $0.1<I_{\text{rel}}^{e}<0.2$)
and one further away ($0.25<I_{\text{rel}}^{\mu}<0.5$ and $0.2<I_{\text{rel}}^{e}<0.5$). The results of the fits,
performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_mtfar}
for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
$R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
an overall uncertainty of 12\% in the \etau channel and 4\% in the \mutau channel.
When performing the same fits in the no b-tag and b-tag categories to determine differences between
this pre-categorisation opposite--sign to same--sign ratio, and the ratio as measured in categories it is found that 
the fit is not stable in the b-tag category due to the number of events in this region being too small.
The uncertainty on the ratio is increased for the b-tag category to cover the differences.
The uncertainties are already large enough to cover differences between the pre-categorisation $R_{\text{QCD}}^{\text{OS/SS}}$ and the
fits as performed in the no b-tag category. So $R_{\text{QCD}}^{\text{OS/SS}}$ in the \mutau channel is taken to be
1.18 in both the b-tag and the no b-tag category, with a 60\% uncertainty in the b-tag category and a 4\% uncertainty in the no b-tag category.
In the \etau channel $R_{\text{QCD}}^{\text{OS/SS}}$ is taken to be 1.02 with a 60\% uncertainty in the b-tag category and a 12\% uncertainty
in the no b-tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.180$\pm$0.044.}
\label{fig:mssm_qcdosss_mtnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.184$\pm$0.035.}
\label{fig:mssm_qcdosss_mtfar}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.015$\pm$0.059.}
\label{fig:mssm_qcdosss_etnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
is 1.127$\pm$0.045.}
\label{fig:mssm_qcdosss_etfar}
\end{figure}

\subsubsection{QCD normalisation}
\label{sec:mssm_bkgs_etmt_qcdnorm}
The QCD normalisation is estimated by inverting the opposite-sign requirement
of the di-tau pair in the signal region. The yield is taken from the same--sign
region with otherwise identical cuts to the opposite--sign region. The contributions
from other backgrounds in this region are subtracted to give an estimate of the number
of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
expected in this region is given by
\begin{equation}\label{eqn:wjets_qcdsub}
N_{\text{W,SS SR}} = \frac{N_{\text{MC,SS SR}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}
\end{equation}

@@

\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
\label{sec:mssm_bkgs_qcd_tt}
In the \tautau channel the QCD background is by far the 
dominant background. The normalisation and shape 
of this background are estimated from a sideband with loosened 
isolation requirements with respect to the signal region. 
In the no b-tag category the sideband used is determined
by having the tau with highest \pT~ pass the tight working
point of the tau ID discriminator, as in the nominal selection.
The other hadronic tau in the pair does not pass the tight working point,
but does pass the medium working point. This sideband is 
chosen as it is as close to the signal region as possible, and 
this should minimise biases in the shape of the total transverse mass
distribution. Other backgrounds
in this sideband are subtracted from the observation to give
the QCD estimate. Differences in normalisation due to
the use of a loosened sideband are corrected for by loose-to-tight isolation
scale factor. This correction factor is measured as
\begin{equation}\label{eqn:tautau_qcd}
R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{\text{obs}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{obs}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
\end{equation}
So this takes the ratio between the observed data with other
backgrounds subtracted in the region equivalent to the signal region, but with the
charge requirement of the pair inverted, and the region equivalent to the sideband
with loosened isolation but with the charge requirement on the pair inverted.

An analogous method is used for this estimate in the 
b-tag category, however, the sideband as used for the 
no b-tag category does not contain enough events to 
provide a background estimate. Therefore a sideband where
the highest \pT~tau passes the tight working point of the
tau ID discriminator, and the other tau passes the loose working
point of the discriminator, but not the tight working point, is used.
This sideband is slightly further away from the signal region than the
`tight--medium' sideband. %The bias from using this looser
%sideband has been assessed and has a less than 1$\sigma$ effect.
%FIXME THIS ISN'T VERY USEFUL INFO!

@@

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}. As the 
shape of the total transverse mass distribution depends on the energy of the $\Pgt_{h}$
it is applied as a shape uncertainty. It is applied to the signal samples and to
backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
hadronic taus.
\subsubsection*{Electron energy scale}
The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This affects
the shape of the total transverse mass distribution, and this uncertainty is applied to the
signals and to the \Ztautau background.
\subsubsection*{High-\pT~$\Pgt_{h}$ ID efficiency}
An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
is applied to account for the extrapolation from the tau ID efficiency
measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s \cite{CMS-PAS-HIG-16-037}. This
uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
The shape difference between the nominal, up- and down- shapes for this uncertainty in the no b-tag category
of the \tautau channel can be seen for a high-mass signal sample in figure \ref{fig:mssm_highpttauid_shapes}a and
for the \Ztautau background in figure \ref{fig:mssm_highpttauid_shapes}b. Because the \Ztautau background
has much softer hadronic taus than the high-mass signal sample, the shape-altering effect of this uncertainty
is much smaller.
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$ signal at $m_{\phi} = 3.2$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
\subfloat[\Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ZTT.pdf}}
\end{center}
\caption{Shape-altering effect of the high \pT~tau ID uncertainty in the no b-tag category of the
\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect is much
larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
\pT~than the \Ztautau sample.}
\label{fig:mssm_highpttauid_shapes}
\end{figure}
\subsubsection*{Top quark \pT~reweighting}
To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape
uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
of the correction, ie the difference between applying the correction twice and not applying the correction at all.
\subsubsection*{Drell-Yan shape reweighting}
An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
On the \Wjets background in the \etau and \mutau channels a shape 
uncertainty of $\frac{-20\% \times p_{\text{T}}}{\text{GeV}}$ is 
applied. This uncertainty is derived from variations in the data/MC ratio
for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~ in 
\Wjets events \cite{CMS-PAS-HIG-16-037}.
